Abstractions and exemplars: The measure noun phrase alternation in German

### 2018-10-08 Latex/sections/3corpus.tex
Copy-editing hell.

For the present study, I used the 21 billion token German \textit{Corpus from the Web} (COW) in its 2014 version DECOW14A (\citealp{SchaeferBildhauer2012full}, and \citealp{Schaefer2015b}, as well as \citealp{BiemannEa2013}, and \citealp{SchaeferBildhauer2013}, for overviews of web corpora in general and the methodology of their construction).%
\footnote{The COW corpora (Dutch, English, French, German, Spanish, Swedish) are made available for free at \url{https://www.webcorpora.org}.
At the time of this writing, a newer 2016 version DECOW16A has already been released.}
This corpus was chosen first because the external validity of any study is increased through a more heterogeneous sample \citep[30]{MaxwellDelaney2004}.
DECOW14A clearly has a much more heterogeneous composition compared with the only other very large corpus of German, the DeReKo of the Institute for the German Language \citep{KupietzEa2010}.
DeReKo contains almost exclusively newspaper texts.%
\footnote{It was shown in \cite{BildhauerSchaefer2016} that, for example, the range of topics is much smaller in DeReKo than in DECOW14A.}
The second reason for choosing this particular corpus is that normative grammars often adopt clear positions regarding the grammaticality of either the \NACa\ or the \PGCa.
Thus, newspaper text or any other texts which conform strongly to normative grammars may not represent the alternation phenomenon fully and without bias because authors and proofreaders who must adhere to normative guidelines might explicitly favour one alternative over another.
Web corpora, on the other hand, contain a significant amount of non-standard language from forums and similar sources.
For such reasons, COW corpora have been used in a number of peer-reviewed publications \citep{VanGoethemHiligsmann2014,VanGoethemHuening2015,MuellerS2014,Schaefer2016c,SchaeferSayatz2014,SchaeferSayatz2016,Zimmer2015}.

@@

\begin{table}
  \centering
  \begin{tabular}{llll}
    Unit of reference & Variable                      & Type    & Levels (for factors only) \\
    \midrule
    Document       & Badness                          & numeric &                           \\
                   & Genitives                        & numeric &                           \\
    Sentence       & Cardinal                         & factor  & Yes, No                   \\
                   & \textbf{Construction (response)} & factor  & NACadj, PGCadj            \\
                   & Measurecase                      & factor  & Nom, Acc, Dat             \\
    Kind lemma     & Kindattraction                   & numeric &                           \\
                   & (Kindcollo)                      & numeric &                           \\
                   & Kindfreq                         & numeric &                           \\
		   & Kindgender                       & factor  & Masc, Neut, Fem             \\
    Measure lemma  & Measureattraction                & numeric &                           \\
                   & (Measurecollo)                   & numeric &                           \\
                   & Measureclass                     & factor  & Physical, Container,      \\
                   &                                  &         & Amount, Portion, Rest     \\
                   & Measurefreq                      & numeric &                           \\
  \end{tabular}
  \caption{Annotated variables for the corpus studies}
  \label{tab:variables}
\end{table}

@@

To capture the influence of style mentioned in Section~\ref{sec:analyses}, two proxy variables were used.
At the document level, the DECOW14A corpus has an annotation for \textit{Badness}.
As described in \cite{SchaeferEa2013}, \textit{Badness} measures how well the distribution of highly frequent short words in the document matches a language model of standard German.
The paper also shows that the Badness score corresponds robustly with human raters' intuitions about text coherence and text quality.
Documents with higher Badness usually contain more incoherent language and shorter sentences.
If the \PGCa\ actually favours more elaborate stylistic levels, a high \textit{Badness} should be correlated with fewer occurrences.
Documents in DECOW14 have also been annotated with a variable called \textit{Genitives}.
For each document it is the case that the higher the values of this variable, the lower the proportion of genitives among all case-bearing forms.
A high number of genitives is also indicative of a more formal, elaborate style close to the written standard.
However, since the \PGCa\ contains a genitive itself, the regressor variable \textit{Genitive} and the document-level variable \textit{Genitives} are not fully independent.
Since instances of the \PGCa\ make up for only a minute fraction of all genitives, I still use \textit{Genitives} as a regressor with the appropriate caveats.

@@

\subsection{Pre-study: main prototype effects in the non-alternating constructions}
\label{sec:prestudy}

@@

\begin{table}
  \centering
  \resizebox{\textwidth}{!}{
    \begin{tabular}{llrlrrrc}
    Model level  & Regressor         & $\text{p}_{\text{PB}}$ & Factor level & Coefficient & CI low & CI high & CI excludes 0 \\
    \midrule
    1                & Badness           & 0.042                  &              &  0.120      & -0.002 &  0.228  &              \\
                     & Cardinal          & 0.001                  & No           &  1.419      &  0.869 &  1.993  &  *           \\
                     & Genitives         & 0.001                  &              & -0.710      & -0.815 & -0.556  &  *           \\[0.5\baselineskip]

@@

  \end{tabular}
  }
  \caption{Coefficient table with 95\% bootstrap confidence intervals for the pre-study; the intercept is -5.370}
  \label{tab:smalltable}
\end{table}

@@

\subsection{Main study: the alternation}
\label{sec:annotation}
\label{sec:corpushierarchicalmodel}

@@

\begin{table}
  \centering
  \resizebox{\textwidth}{!}{
    \begin{tabular}{llrlrrrc}
    Model level  & Regressor         & $\text{p}_{\text{PB}}$ & Factor level & Coefficient & CI low & CI high & CI excludes 0 \\
    \midrule
    1               & Badness           &  0.002                 &              & -0.152      & -0.247 & -0.061  & *             \\
                    & Cardinal          &  0.001                 & No           &  1.189      &  0.862 &  1.466  & *             \\
                    & Genitives         &  0.001                 &              & -0.693      & -0.768 & -0.592  & *             \\
                    & Measurecase       &  0.001                 & Acc          &  0.030      & -0.150 &  0.212  &               \\
                    &                   &                        & Dat          &  0.705      &  0.455 &  0.944  & *             \\[0.5\baselineskip]

@@

  \end{tabular}
  }
  \caption{Coefficient table with 95\% bootstrap confidence intervals for the main study; the intercept is -3.548}
  \label{tab:bigtable}
\end{table}

>>>>

For the present study, I used the 21 billion token German \textit{Corpus from the Web} (COW) in its 2014 version DECOW14A (\citealp{SchaeferBildhauer2012full}, and \citealp{Schaefer2015b}, as well as \citealp{BiemannEa2013}, and \citealp{SchaeferBildhauer2013alt}, for overviews of web corpora in general and the methodology of their construction).%
\footnote{The COW corpora (Dutch, English, French, German, Spanish, Swedish) are made available for free at \url{https://www.webcorpora.org}.
At the time of this writing, a newer 2016 version DECOW16A has already been released.}
This corpus was chosen first because the external validity of any study is increased through a more heterogeneous sample \citep[30]{MaxwellDelaney2004}.
DECOW14A clearly has a much more heterogeneous composition compared with the only other very large corpus of German, the DeReKo of the Institute for the German Language \citep{KupietzEa2010}.
DeReKo contains almost exclusively newspaper texts.%
\footnote{It was shown in \citet{BildhauerSchaefer2016} that, for example, the range of topics is much smaller in DeReKo than in DECOW14A.}
The second reason for choosing this particular corpus is that normative grammars often adopt clear positions regarding the grammaticality of either the \NACa\ or the \PGCa.
Thus, newspaper text or any other texts which conform strongly to normative grammars may not represent the alternation phenomenon fully and without bias because authors and proofreaders who must adhere to normative guidelines might explicitly favour one alternative over another.
Web corpora, on the other hand, contain a significant amount of non-standard language from forums and similar sources.
For such reasons, COW corpora have been used in a number of peer-reviewed publications \citep{VanGoethemHiligsmann2014,VanGoethemHuening2015,MuellerS2014,Schaefer2016c,SchaeferSayatz2014,SchaeferSayatz2016,Zimmer2015}.

@@

\begin{table}
  \centering
  \caption{Annotated variables for the corpus studies}
  \begin{tabular}{llll}
    Unit of reference & Variable                      & Type    & Levels (for factors only) \\
    \midrule
    Document       & Badness                          & numeric &                           \\
                   & Genitives                        & numeric &                           \\
    Sentence       & Cardinal                         & factor  & Yes, No                   \\
                   & \textbf{Construction (response)} & factor  & NACadj, PGCadj            \\
                   & Measurecase                      & factor  & Nom, Acc, Dat             \\
    Kind lemma     & Kindattraction                   & numeric &                           \\
                   & (Kindcollo)                      & numeric &                           \\
                   & Kindfreq                         & numeric &                           \\
		   & Kindgender                       & factor  & Masc, Neut, Fem             \\
    Measure lemma  & Measureattraction                & numeric &                           \\
                   & (Measurecollo)                   & numeric &                           \\
                   & Measureclass                     & factor  & Physical, Container,      \\
                   &                                  &         & Amount, Portion, Rest     \\
                   & Measurefreq                      & numeric &                           \\
  \end{tabular}
  \label{tab:variables}
\end{table}

@@

To capture the influence of style mentioned in Section~\ref{sec:analyses}, two proxy variables were used.
At the document level, the DECOW14A corpus has an annotation for \textit{Badness}.
As described in \citet{SchaeferEa2013}, \textit{Badness} measures how well the distribution of highly frequent short words in the document matches a language model of standard German.
The paper also shows that the Badness score corresponds robustly with human raters' intuitions about text coherence and text quality.
Documents with higher Badness usually contain more incoherent language and shorter sentences.
If the \PGCa\ actually favours more elaborate stylistic levels, a high \textit{Badness} should be correlated with fewer occurrences.
Documents in DECOW14 have also been annotated with a variable called \textit{Genitives}.
For each document it is the case that the higher the values of this variable, the lower the proportion of genitives among all case-bearing forms.
A high number of genitives is also indicative of a more formal, elaborate style close to the written standard.
However, since the \PGCa\ contains a genitive itself, the regressor variable \textit{Genitive} and the document-level variable \textit{Genitives} are not fully independent.
Since instances of the \PGCa\ make up for only a minute fraction of all genitives, I still use \textit{Genitives} as a regressor with the appropriate caveats.

@@

\subsection{Pre-study: Main prototype effects in the non-alternating constructions}
\label{sec:prestudy}

@@

\begin{table}
  \centering
  \caption{Coefficient table with 95\% bootstrap confidence intervals for the pre-study; the intercept is -5.370}
  \resizebox{\textwidth}{!}{
    \begin{tabular}{llrlrrrc}
    Model level  & Regressor         & $\text{p}_{\text{PB}}$ & Factor level & Coefficient & CI low & CI high & CI excludes 0 \\
    \midrule
    1                & Badness           & 0.042                  &              &  0.120      & -0.002 &  0.228  &              \\
                     & Cardinal          & 0.001                  & No           &  1.419      &  0.869 &  1.993  &  *           \\
                     & Genitives         & 0.001                  &              & -0.710      & -0.815 & -0.556  &  *           \\[0.5\baselineskip]

@@

  \end{tabular}
  }
  \label{tab:smalltable}
\end{table}

@@

\subsection{Main study: The alternation}
\label{sec:annotation}
\label{sec:corpushierarchicalmodel}

@@

\begin{table}
  \centering
  \caption{Coefficient table with 95\% bootstrap confidence intervals for the main study; the intercept is -3.548}
  \resizebox{\textwidth}{!}{
    \begin{tabular}{llrlrrrc}
    Model level  & Regressor         & $\text{p}_{\text{PB}}$ & Factor level & Coefficient & CI low & CI high & CI excludes 0 \\
    \midrule
    1               & Badness           &  0.002                 &              & -0.152      & -0.247 & -0.061  & *             \\
                    & Cardinal          &  0.001                 & No           &  1.189      &  0.862 &  1.466  & *             \\
                    & Genitives         &  0.001                 &              & -0.693      & -0.768 & -0.592  & *             \\
                    & Measurecase       &  0.001                 & Acc          &  0.030      & -0.150 &  0.212  &               \\
                    &                   &                        & Dat          &  0.705      &  0.455 &  0.944  & *             \\[0.5\baselineskip]

@@

  \end{tabular}
  }
  \label{tab:bigtable}
\end{table}

### 2018-10-08 Latex/sections/4experiments.tex
Final final final touches.
Copy-editing hell.

\subsection{Experiment 1: forced-choice}
\label{sec:exp:fc}

@@

The first experiment tests preferences for constructions explicitly in a forced-choice task.
Participants had to choose between two sentences that differed only in that one contained the \NACa\, and the other one contained the \PGCa.
In the analysis, the probabilities assigned to the stimuli by the corpus-derived model were compared to the frequency with which participants chose the alternants.
There participants were 24 native speakers of German without reading or writing disabilities, aged 19 to 30, and living permanently in Berlin.
They were recruited from introductory linguistics courses at Freie Universität Berlin.
Although the experiment was conducted in the last four weeks of their first semester, participants had no deeper knowledge of linguistics, grammar, or experimental methods.
None of them had ever participated in a forced-choice experiment before.
Participation was voluntary, but participants received credit in partial fulfillment of course requirements.

@@

\begin{table}
  \centering
  \begin{tabular}[h]{lll}
     & Masculine\slash Neuter & Feminine \\
     \midrule
     \textbf{high prob.\ for PGC\Subsf{adj}} & 4 sentences & 4 sentences \\
     \textbf{low prob.\ for PGC\Subsf{adj}} & 4 sentences & 4 sentences \\
  \end{tabular}
  \caption{The four groups of sentences chosen as stimuli; in each group of four sentences, combinations of important factor values were made unique whenever possible}
  \label{tab:experiment1:design}
\end{table}

The final pairs of stimuli were the sentences containing the attested and preferred alternant (according to the corpus GLMM) and a modified version containing the dispreferred alternant.
They were presented next to each other, and a 20 second time limit for each choice was set.%
\footnote{No participant ever exceeded the time limit.}
The order of sentences was randomised for each participant, and the position of the alternants on the screen (left\slash right) was randomised per participant and sentence.
As fillers, 23 pairs of sentences exemplifying similar but unrelated alternation phenomena from German morpho-syntax were used.
Thus, participants saw 39 pairs of sentences and 78 sentences in total.
They were instructed to select from each pair of sentences the one that seemed more natural to them in the sense that they would use it rather than the other one.
The experiment was conducted using \textit{PsychoPy} \citep{Peirce2007}.

@@

In retrospect, this stimulus was badly chosen because \textit{heiße Luft} `ado' (literally `hot air') is a fixed metaphorical expression.
This obviously influences the reactions of participants, and a revised and improved experiment might lead to a much better fit in future research.%
\footnote{Since I am convinced that the statistical analysis of an experiment has to be determined as part of the experiment's design before the experiment is conducted, removing the data points corresponding to the problematic stimulus from the analysis is not an option.
Future experiments with improved stimuli is the proper route to take.}

@@

\subsection{Experiment 2: self-paced reading}
\label{sec:exp:spr}

@@

The second experiment was conducted in a more implicit paradigm.
It is expected that reading less typical alternants in a given context and with given lexical material incurs a processing overhead for the reader (\citealp{Kaiser2013}).
In this section, a self-paced reading experiment is presented.
In a very similar fashion, \cite{DivjakEa2016} apply the self-paced reading paradigm in the validation of corpus-based models.
The analysis compares the corpus-derived probabilities with potential lags in reading time for sentences with the preferred and the non-preferred constructions.

@@

\begin{table}
  \centering
  \begin{tabular}{lrrrc}
    Regressor & \multicolumn{1}{r}{Coefficient} & \multicolumn{1}{r}{CI low} & \multicolumn{1}{r}{CI high} & \multicolumn{1}{r}{CI excludes 0} \\ \midrule
    Construction=PGCadj                 &  0.054 &  0.012 &  0.095 &  *  \\ 
    Modelprediction                     & -0.003 & -0.113 &  0.110 &     \\ 
    Position                            & -0.005 & -0.005 &  0.004 &     \\ 
    Construction=PGCadj:Modelprediction & -0.125 & -0.234 & -0.023 &  *  \\ 
  \end{tabular}
  \caption{Fixed effect coefficient table for the LMM used to analyse the self-paced reading experiment; the intercept is 0.829}
  \label{tab:exp:spr}
\end{table}

>>>>

\subsection{Experiment 1: Forced-choice}
\label{sec:exp:fc}

@@

The first experiment tests preferences for constructions explicitly in a forced-choice task.
Participants had to choose between two sentences that differed only in that one contained the \NACa\, and the other one contained the \PGCa.
In the analysis, the probabilities assigned to the stimuli by the corpus-derived model were compared to the frequency with which participants chose the alternants.
The participants were 24 native speakers of German without reading or writing disabilities, aged 19 to 30, and living permanently in Berlin.
They were recruited from introductory linguistics courses at Freie Universität Berlin.
Although the experiment was conducted in the last four weeks of their first semester, participants had no deeper knowledge of linguistics, grammar, or experimental methods.
None of them had ever participated in a forced-choice experiment before.
Participation was voluntary, but participants received credit in partial fulfillment of course requirements.

@@

\begin{table}
  \centering
  \caption{The four groups of sentences chosen as stimuli; in each group of four sentences, combinations of important factor values were made unique whenever possible}
  \begin{tabular}[h]{lll}
     & Masculine\slash Neuter & Feminine \\
     \midrule
     \textbf{high prob.\ for PGC\Subsf{adj}} & 4 sentences & 4 sentences \\
     \textbf{low prob.\ for PGC\Subsf{adj}} & 4 sentences & 4 sentences \\
  \end{tabular}
  \label{tab:experiment1:design}
\end{table}

The final pairs of stimuli were the sentences containing the attested and preferred alternant (according to the corpus GLMM) and a modified version containing the dispreferred alternant.
They were presented next to each other, and a 20 second time limit for each choice was set.%
\footnote{No participant ever exceeded the time limit.}
The order of sentences was randomised for each participant, and the position of the alternants on the screen (left\slash right) was randomised per participant and sentence.
As fillers, 23 pairs of sentences exemplifying similar but unrelated alternation phenomena from German morphosyntax were used.
Thus, participants saw 39 pairs of sentences and 78 sentences in total.
They were instructed to select from each pair of sentences the one that seemed more natural to them in the sense that they would use it rather than the other one.
The experiment was conducted using \textit{PsychoPy} \citep{Peirce2007}.

@@

\noindent In retrospect, this stimulus was badly chosen because \textit{heiße Luft} `ado' (literally `hot air') is a fixed metaphorical expression.
This obviously influences the reactions of participants, and a revised and improved experiment might lead to a much better fit in future research.%
\footnote{Since I am convinced that the statistical analysis of an experiment has to be determined as part of the experiment's design before the experiment is conducted, removing the data points corresponding to the problematic stimulus from the analysis is not an option.
Future research with improved stimuli is the proper route to take.}

@@

\subsection{Experiment 2: Self-paced reading}
\label{sec:exp:spr}

@@

The second experiment was conducted in a more implicit paradigm.
It is expected that reading less typical alternants in a given context and with given lexical material incurs a processing overhead for the reader (\citealp{Kaiser2013}).
In this section, a self-paced reading experiment is presented.
In a very similar fashion, \citet{DivjakEa2016} apply the self-paced reading paradigm in the validation of corpus-based models.
The analysis compares the corpus-derived probabilities with potential lags in reading time for sentences with the preferred and the non-preferred constructions.

@@

\begin{table}
  \centering
  \caption{Fixed effect coefficient table for the LMM used to analyse the self-paced reading experiment; the intercept is 0.829}
  \begin{tabular}{lrrrc}
    Regressor & \multicolumn{1}{r}{Coefficient} & \multicolumn{1}{r}{CI low} & \multicolumn{1}{r}{CI high} & \multicolumn{1}{r}{CI excludes 0} \\ \midrule
    Construction=PGCadj                 &  0.054 &  0.012 &  0.095 &  *  \\ 
    Modelprediction                     & -0.003 & -0.113 &  0.110 &     \\ 
    Position                            & -0.005 & -0.005 &  0.004 &     \\ 
    Construction=PGCadj:Modelprediction & -0.125 & -0.234 & -0.023 &  *  \\ 
  \end{tabular}
  \label{tab:exp:spr}
\end{table}

### 2018-10-08 Latex/sections/5conclusions.tex
Copy-editing hell.

Many relevant conclusions can be drawn based on the research presented here.
Although direct inferences from corpus data to mental representations are problematic (see Section~\ref{sec:cogocl}), the two attraction features (\textit{Kindattraction} and \textit{Measureattraction}) are virtually impossible to conceive of as prototype effects and thus favour an exemplar view or a mixed exemplar-prototype view.
As discussed in Section~\ref{sec:cogocl}, it is unnecessary to follow an extreme route, be it radical prototype theory or radical exemplar theory, given recent developments in cognitive science and cognitive linguistics.
While it is surely an intentionally overstated comment, \citet[15]{Kapatsinski2014} even suggests that ``[i]n the extreme, some speakers’ heads could host exemplar models, and some could contain fairly abstract grammars, and the produced output would be essentially identical''.
If this is the case (even to a less extreme degree), corpora only provide pooled data averaged over speaker grammars with varying levels of abstraction.
Clearly, more research is required in this direction.

@@

\begin{quote}
  There are now a number of published multivariate models that use data[,] extracted from corpora [\ldots] to predict the choice for one morpheme, lexeme or construction over another.
  However, [\ldots] only a small number of these corpus-based studies have been cross-validated [\ldots].
  Of these cross-validated studies, few have directly evaluated the prediction accuracy of a complex, multivariate corpus-based model on humans using authentic corpus sentences [\ldots].
\end{quote}

@@

On a larger methodological scale, this paper also makes a number of contributions.
The statistical model was a true multilevel model (see Section~\ref{sec:mainstudystatisticalmodel}), demonstrating how multilevel modelling helps to specify complex hierarchies of abstract features, item-specific tendencies, and exemplar effects at the level of observations (sentences; first level) and lemmas (second level).
\cite{Gries2015} still calls mixed models ``underused'' in corpus linguistics, and multilevel models are consequently also an underused tools.
At the same time, the ill effects of overparametrisation of mixed models with varying slopes as criticised by \cite{BatesEa2015a} were demonstrated.
Furthermore, fitting an additive model to the reading time data did not improve the fit as there were no non-linearities in the data.
While \cite{DivjakEa2016} also use attested sentences, they find that an additive model helped to deal with non-linearities.
This is clearly another area where only more studies can lead to clarification.
Finally, much like \cite{Dabrowska2014} found that speakers' knowledge of collocations was not matched by a set of standard measures of collocation strength extracted from corpora, a simple quotient based on raw frequencies for the attraction strength performed much better in the present study compared to collexeme strength in the form of logarithmised Fisher p-values. 
While this does not allow the conclusion that collexeme strength has no cognitive reality, it might indicate that for measuring attraction effects exerted by non-alternating constructions on alternating constructions, taking the marginals into account might not be crucial.%
\footnote{However, many different measures have been proposed within the collostructional framework (see \citealp{Gries2015b} for an overview of them and a defense of the framework).
Future research might show significant differences between them for the problem at hand.}

@@

In closing, I want to point out that the so-called \textit{case of doubt} in German morpho-syntax -- like the measure noun phrase alternation -- are in fact ideal test cases for probabilistic modelling of alternation phenomena in cognitive linguistics.
Doing more research on them could help to provide answers to many of the fundamental and methodological issues raised here.

>>>>

Many relevant conclusions can be drawn based on the research presented here.
Although direct inferences from corpus data to mental representations are problematic (see Section~\ref{sec:cogocl}), the two attraction features (\textit{Kindattraction} and \textit{Measureattraction}) are virtually impossible to conceive of as prototype effects and thus favour an exemplar view or a mixed exemplar-prototype view.
As discussed in Section~\ref{sec:cogocl}, it is unnecessary to follow an extreme route, be it radical prototype theory or radical exemplar theory, given recent developments in cognitive science and cognitive linguistics.
While it is surely an intentionally overstated comment, \citet[15]{Kapatsinski2014} even suggests that ``in the extreme, some speakers’ heads could host exemplar models, and some could contain fairly abstract grammars, and the produced output would be essentially identical''.
If this is the case (even to a less extreme degree), corpora only provide pooled data averaged over speaker grammars with varying levels of abstraction.
Clearly, more research is required in this direction.

@@

\begin{quote}
  There are now a number of published multivariate models that use data, extracted from corpora [\ldots] to predict the choice for one morpheme, lexeme or construction over another.
  However, [\ldots] only a small number of these corpus-based studies have been cross-validated [\ldots].
  Of these cross-validated studies, few have directly evaluated the prediction accuracy of a complex, multivariate corpus-based model on humans using authentic corpus sentences [\ldots].
\end{quote}

@@

On a larger methodological scale, this paper also makes a number of contributions.
The statistical model was a true multilevel model (see Section~\ref{sec:mainstudystatisticalmodel}), demonstrating how multilevel modelling helps to specify complex hierarchies of abstract features, item-specific tendencies, and exemplar effects at the level of observations (sentences; first level) and lemmas (second level).
\citet{Gries2015} still calls mixed models ``underused'' in corpus linguistics, and multilevel models are consequently also an underused tools.
At the same time, the ill effects of overparametrisation of mixed models with varying slopes as criticised by \citet{BatesEa2015a} were demonstrated.
Furthermore, fitting an additive model to the reading time data did not improve the fit as there were no non-linearities in the data.
While \citet{DivjakEa2016} also use attested sentences, they find that an additive model helped to deal with non-linearities.
This is clearly another area where only more studies can lead to clarification.
Finally, much like \citet{Dabrowska2014} found that speakers' knowledge of collocations was not matched by a set of standard measures of collocation strength extracted from corpora, a simple quotient based on raw frequencies for the attraction strength performed much better in the present study compared to collexeme strength in the form of logarithmised Fisher p-values. 
While this does not allow the conclusion that collexeme strength has no cognitive reality, it might indicate that for measuring attraction effects exerted by non-alternating constructions on alternating constructions, taking the marginals into account might not be crucial.%
\footnote{However, many different measures have been proposed within the collostructional framework (see \citealp{Gries2015b} for an overview of them and a defense of the framework).
Future research might show significant differences between them for the problem at hand.}

@@

In closing, I want to point out that the so-called cases of doubt in German morphosyntax -- like the measure noun phrase alternation -- are in fact ideal test cases for probabilistic modelling of alternation phenomena in cognitive linguistics.
Doing more research on them could help to provide answers to many of the fundamental and methodological issues raised here.
